---
title: "p8105_hw1_rh3195"
author: "Ruijie He"
date: "2023-09-23"
output:
  pdf_document: default
  html_document: default
---

## Problem 1
```{r}
library ("moderndive")
data("early_january_weather")
```
# variables in dataset
```{r} 
variables <- colnames(early_january_weather)
variables
```
# Size of dataset
```{r}
num_rows <- nrow(early_january_weather)
num_cols <- ncol(early_january_weather)
num_rows
```
```{r}
num_cols
```
```{r}
mean_temp <- mean (early_january_weather$temp)
mean_temp
```

- There are 15 variables in this dataset. Some important variables including year, month, day, and time_hour that tells the time. The wind direction, wind speed, and wind-gust that is related to the wind. Also the "temp" tells temperature and "humid" tells the humidity. It has 358 rows and 15 columns. The mean temperature is 39.58 degree.
# Making scatterplot of temp (y) vs. time_hour (x)
```{r}
library (ggplot2)

ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(x = "Time_hour", y = "Temp", color = "Humid") +
  ggtitle("Scatterplot of time_hour vs. Temperature") +
  theme_minimal()
```
##Describe pattern of scatterplot##

- The scatterplot shows that the two variables time_hour and tempeartue are having a positive association. Because as the temperature increases as the time_hour do. And the data points on this plot are assembled closely nearly to a linear line, which illustrating a linear relationship.
```{r}
ggsave("scatterplot_of_time_vs_temperature.pdf", width = 6, height =4)
```

## Problem 2
```{r}
library (tidyverse)
```
```{r}
my_df =
  tibble(
    vec_numeric = rnorm (10),
   vec_logical = vec_numeric > 0,
   vec_char = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
   vec_factor = factor(
     sample(c("L0", "L1", "L2"), 10, rep = TRUE)
   )
  )
print (my_df)
```
```{r}
mean_numeric = mean(pull(my_df, vec_numeric))
mean_logical = mean(pull(my_df, vec_logical))
mean_char = mean(pull(my_df, vec_char))
mean_factor = mean(pull(my_df, vec_factor))
print (mean_numeric)
print (mean_logical)
print (mean_char)
print (mean_factor)
```
- The variable of vec_numeric and vec_logical have mean. Charactor variable and factor variable do not generates mean because they are not numeric number or logical.

```{r}
as.numeric(pull(my_df, vec_logical))
as.numeric(pull(my_df, vec_char))
as.numeric(pull(my_df, vec_factor))
```
- The vec_logical is converted to binary datapoints where 0 is false and 1 is true. The vec_factor also get translated to 3 categories based on given lavels. The only variable that is unable to convert to numeric is the vec_char. This helps me to understand what happens when trying to take the mean. It tells that mean should be numeric numbers.
